Centralizers of higher enveloping algebras of Lie algebras

### 2020-08-30 draft.tex
rearrangments before cleaning up strictified stuff

@@

\begin{thm}
\label{thm: centralizer}
Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and let 
\[
f: \UU_n \fg \to B
\]
be a map of augmented $E_n$ algebras.
Then
\begin{itemize}
\item $f$ equips $B$ with the structure of an $E_n$ algebra in $\fg$-modules and
\item the centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the Chevalley-Eilenberg 
cochains $\clies(\fg, B)$ equipped with the convolution $E_n$-product.
\end{itemize}
\end{thm}

@@

\subsection{Maps out of enveloping $E_n$ algebras}

\owen{I might move the discussion of $E_n$-modules from near proposition~\ref{P:ModentoModSn} to here. 
We can then sketch here the argument you explained about $E_n$-monoidal products to show that $B$ lifts to an $E_n$ algebra $B_f$ in $\fg$-modules.}

\begin{prp}
Let $\Ch_k^{\otimes_k}$ be the symmetric monoidal $\infty$-category arising from cochain complexes of vector spaces over a characteristic zero field $k$.
Let $\fg$ be a Lie algebra in $\Ch_k^{\otimes_k}$, i.e., a dg Lie algebra, 
and let $B$ be an $E_n$ algebra in $\Ch_k^{\otimes_k}$.
Then given a map of $E_n$ algebras $f: \UU_n \fg \to B$, 
there exists a lift of $B$ to an $E_n$ algebra $B_f$ in $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k}$, the symmetric monoidal $\infty$-category of $\fg$-modules.
\end{prp}

\begin{proof}
By Corollary 3.4.4.6 of \cite{LurieHA}, any $E_n$ algebra $B$ defines an $E_n$-monoidal category ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ of $E_n$-$B$-modules. 
Furthermore, by Corollary 3.4.1.7 \cite{LurieHA} (see also Example 3.4.4.7 of the same reference) $B$ can be viewed as an $E_n$-algebra in this $E_n$-monoidal category. 
In other words, there is an object $\Bar{B} \in  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ which gets sent to $B$ under the forgetful functor ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k}) \to \Ch_k^{\otimes_k}$.

Given a map of $E_n$-algebras $f : A \to B$ there is an $E_n$-monoidal functor of $E_n$-module categories 
\[
f^* :  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes_k}) \to  {\rm Mod}_A^{E_n} (\Ch_k^{\otimes_k}) .
\]
In particular, for $A = \UU_n \fg$, we see that the $E_n$-algebra $B$ defines an $E_n$-algebra object $f^*\Bar{B} \in {\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes k})$. 
Again, the image of this object under the forgetful functor to $\Ch_k^{\otimes_k}$ is $B$.

Now, for any $E_n$-algebra the factorization homology along the $(n-1)$-sphere $\int_{S^{n-1}} A$ is an $E_1$-algebra.
By Proposition 3.33 of \cite{FrancisHH} (see also Example 5.5.4.16 of \cite{LurieHA}), there is an equivalence of $\infty$-categories ${\rm Mod}^{E_n}_A (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\int_{S^{n-1}} A} (\Ch_k^{\otimes_k})$.
For $A = \UU_n \fg$, the factorization homology along the $(n-1)$-sphere is $\int_{S^{n-1}} A \simeq \UU_1 \left(\fg[\epsilon] \right)$, where $\epsilon$ is a formal parameter of cohomological degree $n-1$.
It follows that there is an equivalence of $\infty$-categories 
\[
{\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\UU_1(\fg[\epsilon])} (\Ch_k^{\otimes_k}) = {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k}) .
\]
\brian{The RHS has a symmetric monoidal structure with $\otimes_k$. 
This does not agree with the tensor product on the LHS, but we hope there is a functor $\otimes_{\UU_n \fg} \to \otimes_k$.}

Finally, restriction along the map of Lie algebras $i : \fg \hookrightarrow \fg[\epsilon]$ defines monoidal functor $i^* :  {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k})  \to  {\rm Mod}_{\fg} (\Ch_k^{\otimes_k})$. 
The desired $E_n$-algebra object $B_f$ is $i^* f^* \Bar{B}$.
\end{proof}

By the strictification results, $B_f$ admits a model ${\tt B}_f$ as a strict prefactorization algebra with values in the stable symmetric monoidal \owen{other adjectives} model category $\Alg_\Lie(\Ch_k^{\rm dg})$.
As the forgetful functor $\Alg_\Lie(\Ch_k^{\rm dg}) \to \Alg_\Lie(\Ch_k^{\rm dg})$ is \owen{more adjectives},
we obtain an underlying strict prefactorization algebra ${\tt B}$ with values in cochain complexes.
Moreover, there is a canonical map $\cliel(\fg[-n]) \to {\tt B}$ of strict prefactorization algebras that models $f$, as desired.

\owen{I'd love to say we can produce a map from our favorite model of the envelope, but we may not need it.}

@@

\section{Strictifying the map $f: \UU_n \fg \to B$}

\owen{If our new strategy works, then we can get rid of this section.}

As a first step, we analyze the strictification of the map $f: \UU_n \fg \to B$ and show how it lets us view $B$ as an $E_n$ algebra in~$\Ch(\Rep(\fg))$.

By using the small model \owen{see my comment \ref{note on little model}}, we can strictify to obtain a map
\[
{\tt f}: \cliel(\fg[-n]) \to {\tt B}.
\]

\owen{And now I'm really confused.}

\owen{I'm not wild about Greg's phrasing below. Also, I'd prefer to move the explicit formulas later, when we've shifted our setting to strict prefactorization algebras.}

\begin{rmk}
It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to $\Sigma^{n-1}B = B[n-1]$. 
Henceforth in this paper, we will simply use the notation $B[n-1]$ for $\oblv_n(B)$, 
that is tacitly assume we $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
\end{rmk}

Let  $f:\UU_n \fg \to B$ be an $E_n$-algebra map. Then the adjunction 
\[
\xymatrix{\Alg_\Lie(\Mod_k) \ar@/^/[r]^{\UU_n} & \ar[l]^{\oblv_n}  \Alg_{E_n}(\Mod_k)}
\]
gives a $L_\infty$-algebra morphism 
\begin{equation}
 \tilde{f}: \fg \, \longrightarrow \, \oblv(B)\cong B[n-1]
\end{equation}
which makes $B[n-1]$ into a $\fg$-module and therefore its shift $B$ inherits a  $\fg$-module structure as well from $f$.

\brian{let's start with a strict representative $B$. 
So we have an actual locally constant factorization algebra.}

\begin{prp}\label{P:inducedEngModStruct} Let $f:\UU_n \fg \to B$ be an $E_n$-algebra morphism. 
The induced $\fg$ $L_\infty$-module on $B$ lifts canonically to make  $B$ into an $E_n$-algebra in the category of $\fg$-modules that we denote by $B_f$. 
\end{prp}
\begin{proof}

\end{proof}
Proposition~\ref{P:inducedEngModStruct} has an easy realization in the factorization algebra setting.
Indeed, applying the equivalence of $E_n$-algebras with locally constant factorization algebras (Theorem~\ref{T:En=Fac}), 
we obtain an induced map of factorization 
algebras 
\begin{equation}\label{eq:DefofFonFaclevel}
 \mathbf{f}: \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow B(-)
\end{equation}
 where $B(-)$ is the factorization algebra associated to $B$.
 \brian{How about $\ul{B}$ instead?}

\begin{lmm}\label{L:inducedFacgModstruct} The factorization algebra map  $\mathbf{f}$ makes $B(-)$ into an homotopy cosheaf of $L_\infty$-modules over 
 $\fg \otimes \Omega^*_c(-)$.
\end{lmm}
\begin{proof}

\end{proof}
The lemma allows us to define the factorization algebra given on any open $U$ by  the Chevalley-Eilenberg chain complexes
$ \cliels\big(\fg \otimes \Omega^*_c(U), B(U) \big)$ (with their standard differential)
of $\fg \otimes \Omega^*_c(U)$ with value on $B(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
a finite family of pairwise disjoint open subsets of an open $V$, by 
\begin{multline}\label{eq:transClieFac}
 \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), B(U_i) \big) \cong Sym\Big(
 \fg\otimes (\bigoplus_{i\in I}  \Omega^*_c(U_i))[-1]  \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big) \\ 
 \cong Sym\Big(\fg\otimes \Omega_c\big(\coprod U_i\big)[-1] \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big)  
 \stackrel{\omega^*\otimes \mu_B}\longrightarrow Sym(\fg\otimes \Omega_c(V)[-1] ) \otimes B(V) \\ 
 = \cliels(\fg\otimes \Omega_c(V), B(V))
\end{multline}
where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B(-)$.

The (homotopy) sheaf structure of forms also gives us structure maps
\begin{multline}\label{eq:transClieFacCochain}
 \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\mu_B}\longrightarrow 
  \clies(\fg\otimes \Omega (V), B(V))
\end{multline}
where $\rho$ is given by the restriction of forms onto a subspace.

\begin{lmm}\label{L:ClieFacDef} For any (resp. locally constant) factorization algebra $B(-)$ and factorization algebra map $\mathbf{f}:\UU_n(\fg) \to B(-)$, 
 the structure maps~\eqref{eq:transClieFac} makes $ \cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
 Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
 $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
\end{lmm}
\begin{dfn}\label{dfn:CEofFact}
We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.
\end{dfn}
\begin{proof}

A special but very interesting case is of course when $B$ is itself an enveloping algebra. 
\begin{cor}
 Let $\fg$, $\fh$ be dg-Lie algebras and $f:\fg\to \fh$ be a dg-Lie algebra morphism. 
 Then the induced factorization algebra map $\mathbf{\UU_n f}:  \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow  \cliels( \fh \otimes \Omega^*_c(-)) $
 is the standard map $\cliels(f)$ induced by $f$ and the action of $\fg  \otimes \Omega^*_c(-)$ is obtained from the $\fg$-action on $\fh$ by Leibniz rule.
\end{cor}
\begin{rmk}\greg{Extends to $L_\infty$ case in a sentence or too}
\end{rmk}

>>>>

\owen{We should collect here a list of notations, such as}

Let $\Ch_k^{\otimes_k}$ be the symmetric monoidal stable $\infty$-category arising from cochain complexes of vector spaces over a characteristic zero field $k$.
Let ${\tt Ch}_k^{\otimes_k}$ denote the symmetric monoidal stable model category of cochain complexes of vector spaces over a characteristic zero field $k$ ETC.

@@

\begin{thm}
\label{thm: centralizer}
Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and let 
\[
f: \UU_n \fg \to B
\]
be a map of augmented $E_n$ algebras.
Then
\begin{itemize}
\item $f$ lets us lift $B$ to an $E_n$ algebra $B_f$ in $\fg$-modules and
\item the centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the Chevalley-Eilenberg 
cochains $\clies(\fg, B_f)$ equipped with the convolution $E_n$-product.
\end{itemize}
\end{thm}

@@

@@

\section{Lifting $B$ to an $E_n$ algebra $B_f$ in $\fg$-modules}

A technical result is the key step.

\def\obl{{\rm obl}}

\begin{prp}
\label{prp: def of obl}
For $\fg$ a dg Lie algebra in $\Ch_k^{\otimes_k}$, i.e., a dg Lie algebra, 
there is a forgetful functor $\obl: \Mod^{E_n}_{\UU_n \fg} \to \LMod_{U\fg}$ that is lax $E_n$-monoidal.
\end{prp}

\owen{I don't know if we need to include the adjective ``lax'' here, or if it's implicit in the usual discussions these days.}

Concretely, we mean there is a natural morphism
\[
\obl(M) \otimes_k \obl \to \obl(M \otimes_{\UU_n \fg} N) 
\]
as left modules over $U\fg$, i.e., as $\fg$-representations.

As a consequence, we obtain the following.

\begin{cor}
There is a functor 
\[
\Alg_{E_n}(\obl): \Alg_{E_n}({\Mod^{E_n}_{\UU_n \fg}}) \to \Alg_{E_n}(\LMod_{U\fg}).
\]
\end{cor}

\begin{prp}
Let $\fg$ be a Lie algebra in $\Ch_k^{\otimes_k}$, 
and let $B$ be an $E_n$ algebra in $\Ch_k^{\otimes_k}$.
Given a map of $E_n$ algebras $f: \UU_n \fg \to B$, 
there exists a lift of $B$ to an $E_n$ algebra $B_f$ in $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k}$, the symmetric monoidal $\infty$-category of $\fg$-modules.
\end{prp}

\begin{proof}
By Corollary 3.4.4.6 of \cite{LurieHA}, any $E_n$ algebra $B$ defines an $E_n$-monoidal category ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ of $E_n$-$B$-modules with monoidal structure $\otimes_B$. 
Furthermore, by Corollary 3.4.1.7 \cite{LurieHA} $B$ can be viewed as an $E_n$-algebra in this $E_n$-monoidal category. 
(See also Example 3.4.4.7 of the same reference.)
In other words, there is an object $\Hat{B} \in  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ sent to $B$ under the forgetful functor ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k}) \to \Ch_k^{\otimes_k}$.

Given a map of $E_n$-algebras $f : A \to B$, 
the forgetful functor of $E_n$-module categories 
\[
f^* :  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes_k}) \to  {\rm Mod}_A^{E_n} (\Ch_k^{\otimes_k}) .
\]
admits a natural refinement to an $E_n$-monoidal functor.
\owen{Any place to cite?}
In particular, for $A = \UU_n \fg$, there is an $E_n$-algebra object $f^*\Hat{B} \in {\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes k})$, and it forgets to $B$ under the forgetful functor to $\Ch_k^{\otimes_k}$, by construction.

Applying the $E_n$-monoidal functor $\obl$, we obtain an $E_n$ algebra $\obl(f^*\Hat{B})$ in $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k}$.
Again, by construction, it forgets to $B$.
We denote $\obl(f^*\Hat{B})$ by~$B_f$.
\end{proof}

\begin{rmk}
By the strictification results, $B_f$ admits a model ${\tt B}_f$ as a strict prefactorization algebra with values in the stable symmetric monoidal \owen{other adjectives} model category $\Alg_\Lie(\Ch_k^{\rm dg})$.
As the forgetful functor $\Alg_\Lie({\tt Ch}_k) \to \Alg_\Lie({\tt Ch}_k)$ is \owen{more adjectives},
we obtain an underlying strict prefactorization algebra ${\tt B}$ with values in cochain complexes.
Moreover, there is a canonical map $\cliel(\fg[-n]) \to {\tt B}$ of strict prefactorization algebras that models $f$, as desired.
\end{rmk}

It remains to prove the technical result.

\begin{proof}[Proof of proposition~\ref{prp: def of obl}]
\owen{We are stuck on this point.}
We construct the underlying functor of $\infty$-categories $\Mod^{E_n}_{\UU_n \fg} \to \LMod_{U\fg}$ 
before lifting to a lax $E_n$-monoidal functor.

For any $E_n$-algebra the factorization homology along the $(n-1)$-sphere $\int_{S^{n-1}} A$ is an $E_1$-algebra.
By Proposition 3.33 of \cite{FrancisHH} (see also Example 5.5.4.16 of \cite{LurieHA}), 
there is an equivalence of $\infty$-categories ${\rm Mod}^{E_n}_A (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\int_{S^{n-1}} A} (\Ch_k^{\otimes_k})$.
For $A = \UU_n \fg$, the factorization homology along the $(n-1)$-sphere is 
\[
\int_{S^{n-1}} A \simeq \UU_1 \left(\fg[\epsilon] \right),
\] 
where $\epsilon$ is a formal parameter of cohomological degree $n-1$.
It follows that there is an equivalence of $\infty$-categories 
\[
{\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\UU_1(\fg[\epsilon])} (\Ch_k^{\otimes_k}).
% = {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k}) .
\]
Consider now the map of Lie algebras $i : \fg \hookrightarrow \fg[\epsilon]$,
which induces a forgetful functor $i^* :  {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k})  \to  {\rm Mod}_{\fg} (\Ch_k^{\otimes_k})$. 
The composite 
\[
{\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\UU_1(\fg[\epsilon])} (\Ch_k^{\otimes_k}) \xto{i^*}  {\rm LMod}_{U\fg} (\Ch_k^{\otimes_k})
\]
is the desired forgetful functor.

\owen{Now we need to explain why it is lax monoidal.}
\end{proof}

%\section{Strictifying the map $f: \UU_n \fg \to B$}
%
%
%\owen{If our new strategy works, then we can get rid of this section.}
%
%As a first step, we analyze the strictification of the map $f: \UU_n \fg \to B$ and show how it lets us view $B$ as an $E_n$ algebra in~$\Ch(\Rep(\fg))$.
%
%By using the small model \owen{see my comment \ref{note on little model}}, we can strictify to obtain a map
%\[
%{\tt f}: \cliel(\fg[-n]) \to {\tt B}.
%\]
%
%\owen{And now I'm really confused.}
%
%\owen{I'm not wild about Greg's phrasing below. Also, I'd prefer to move the explicit formulas later, when we've shifted our setting to strict prefactorization algebras.}
%
%
%\begin{rmk}
%It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
%the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to $\Sigma^{n-1}B = B[n-1]$. 
%Henceforth in this paper, we will simply use the notation $B[n-1]$ for $\oblv_n(B)$, 
%that is tacitly assume we $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
%\end{rmk}
%
%Let  $f:\UU_n \fg \to B$ be an $E_n$-algebra map. Then the adjunction 
%\[
%\xymatrix{\Alg_\Lie(\Mod_k) \ar@/^/[r]^{\UU_n} & \ar[l]^{\oblv_n}  \Alg_{E_n}(\Mod_k)}
%\]
%gives a $L_\infty$-algebra morphism 
%\begin{equation}
% \tilde{f}: \fg \, \longrightarrow \, \oblv(B)\cong B[n-1]
%\end{equation}
%which makes $B[n-1]$ into a $\fg$-module and therefore its shift $B$ inherits a  $\fg$-module structure as well from $f$.
%
%\brian{let's start with a strict representative $B$. 
%So we have an actual locally constant factorization algebra.}
%
%\begin{prp}\label{P:inducedEngModStruct} Let $f:\UU_n \fg \to B$ be an $E_n$-algebra morphism. 
%The induced $\fg$ $L_\infty$-module on $B$ lifts canonically to make  $B$ into an $E_n$-algebra in the category of $\fg$-modules that we denote by $B_f$. 
%\end{prp}
%\begin{proof}
% 
%\end{proof}
%Proposition~\ref{P:inducedEngModStruct} has an easy realization in the factorization algebra setting.
%Indeed, applying the equivalence of $E_n$-algebras with locally constant factorization algebras (Theorem~\ref{T:En=Fac}), 
%we obtain an induced map of factorization 
%algebras 
%\begin{equation}\label{eq:DefofFonFaclevel}
% \mathbf{f}: \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow B(-)
%\end{equation}
% where $B(-)$ is the factorization algebra associated to $B$.
% \brian{How about $\ul{B}$ instead?}
% 
%\begin{lmm}\label{L:inducedFacgModstruct} The factorization algebra map  $\mathbf{f}$ makes $B(-)$ into an homotopy cosheaf of $L_\infty$-modules over 
% $\fg \otimes \Omega^*_c(-)$.
%\end{lmm}
%\begin{proof}
% 
%\end{proof}
%The lemma allows us to define the factorization algebra given on any open $U$ by  the Chevalley-Eilenberg chain complexes
%$ \cliels\big(\fg \otimes \Omega^*_c(U), B(U) \big)$ (with their standard differential)
%of $\fg \otimes \Omega^*_c(U)$ with value on $B(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
%a finite family of pairwise disjoint open subsets of an open $V$, by 
%\begin{multline}\label{eq:transClieFac}
% \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), B(U_i) \big) \cong Sym\Big(
% \fg\otimes (\bigoplus_{i\in I}  \Omega^*_c(U_i))[-1]  \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big) \\ 
% \cong Sym\Big(\fg\otimes \Omega_c\big(\coprod U_i\big)[-1] \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big)  
% \stackrel{\omega^*\otimes \mu_B}\longrightarrow Sym(\fg\otimes \Omega_c(V)[-1] ) \otimes B(V) \\ 
% = \cliels(\fg\otimes \Omega_c(V), B(V))
%\end{multline}
%where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B(-)$.
%
%\smallskip
%
%The (homotopy) sheaf structure of forms also gives us structure maps
%\begin{multline}\label{eq:transClieFacCochain}
% \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
%  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
% \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
% \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
% \stackrel{\mu_B}\longrightarrow 
%  \clies(\fg\otimes \Omega (V), B(V))
%\end{multline}
%where $\rho$ is given by the restriction of forms onto a subspace. 
%
%\begin{lmm}\label{L:ClieFacDef} For any (resp. locally constant) factorization algebra $B(-)$ and factorization algebra map $\mathbf{f}:\UU_n(\fg) \to B(-)$, 
% the structure maps~\eqref{eq:transClieFac} makes $ \cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
% Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
% $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
%\end{lmm}
%\begin{dfn}\label{dfn:CEofFact}
%We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
%and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.
%\end{dfn}
%\begin{proof}
% 
%\end{proof}
%
%
%A special but very interesting case is of course when $B$ is itself an enveloping algebra. 
%\begin{cor}
% Let $\fg$, $\fh$ be dg-Lie algebras and $f:\fg\to \fh$ be a dg-Lie algebra morphism. 
% Then the induced factorization algebra map $\mathbf{\UU_n f}:  \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow  \cliels( \fh \otimes \Omega^*_c(-)) $
% is the standard map $\cliels(f)$ induced by $f$ and the action of $\fg  \otimes \Omega^*_c(-)$ is obtained from the $\fg$-action on $\fh$ by Leibniz rule.
%\end{cor}
%\begin{rmk}\greg{Extends to $L_\infty$ case in a sentence or too}
%\end{rmk}
%
